---
title: "p8105_hw6_tw2918"
output: github_document
date: "2023-11-20"
---

```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(modelr)
set.seed(1)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Probelm 1

**Import and Clean Dataset**

* update the victim's first and last name to proper case
* replace `unknown` to missing value `NA`
* update `victim_age` to numeric variable
* create new variable `city_state` and `case_resovled`, ane make `case_resovled` numeric
* filter out four `city_state` values
* filter and only keep observations if `victim_race` is white or black. 

```{r}
homicide_df = read_csv("./data/homicide_data.csv", show_col_types = FALSE) |>
  janitor::clean_names()|>
  mutate (
    victim_last = str_to_title(victim_last),
    victim_first = str_to_title(victim_first),
    across(c(uid, victim_last, victim_first, victim_race, victim_age, victim_sex, city, state, disposition), ~na_if(., "Unknown")),
    victim_age = as.numeric(victim_age),
    city_state = paste(city, state, sep = ", "),
    case_resolved = ifelse(grepl("Closed", disposition, ignore.case = TRUE), "1", "0"),
    case_resolved = as.numeric(case_resolved)
    )|>
  filter(
    !city_state %in% c("Tulsa, AL", "Dallas, TX", "Phoenix, AZ", "Kansas City, MO" ),
    victim_race == "White" | victim_race == "Black"
    )

print(homicide_df)
```

**Logistic regression on city of Balitmore, MD**

For the city of `Baltimore, MD`, use the `glm` function to fit a logistic regression with `resolved` vs `unresolved` as the outcome and victim age, sex and race as predictors. Save the output of `glm` as an `R object`; 

```{r}
fit_logistic = homicide_df |>
  filter(city_state == "Baltimore, MD")|>
  glm(case_resolved ~ victim_age + victim_sex + victim_race,data = _, family = binomial())

print(fit_logistic)
```

apply the `broom::tidy` to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.

```{r}
fit_logistic|>
  broom::tidy()|>
  filter(term == "victim_sexMale")|>
  mutate(OR = exp(estimate),
         ci_lower = exp(estimate - (1.96 * std.error)),
         ci_upper = exp(estimate + (1.96 * std.error))
      )|>
  select(term, OR, ci_lower, ci_upper)|>
  knitr::kable(digits = 3)
```

**Logistic regression on each of the city**

run `glm` for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims. Do this within a “tidy” pipeline, making use of `purrr::map`, `list columns`, and `unnest` as necessary to create a dataframe with estimated ORs and CIs for each city.

```{r}
fit_logistic_allcity = homicide_df |>
    nest(df = -city_state)|>
  mutate(
    glm_model = purrr::map(df, \(df) 
                     glm(case_resolved ~ victim_age + victim_sex + victim_race,data =df, family = binomial())),
    glm_result = map (glm_model, broom::tidy)
  )|>
  select(city_state, glm_result)|>
  unnest(glm_result)|>
  filter(term == "victim_sexMale")|>
  mutate(OR = exp(estimate),
         ci_lower = exp(estimate - (1.96 * std.error)),
         ci_upper = exp(estimate + (1.96 * std.error))
      )|>
  select(city_state, OR, ci_lower, ci_upper)

print(fit_logistic_allcity)
```

**Plot for OR and CI**

Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.

```{r}
fit_logistic_allcity |>
  mutate(city_state = reorder(city_state, OR))|>
  ggplot(aes(x=city_state, y =OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper))+
  labs(
    title = "Estimated OR and Confidance Interval of Solving Homicides Comparing Male to Female Victims in Each City ",
    x = "Cities and States",
    y = "Estimated OR",
  ) +
  theme(axis.text.x =element_text(angle = 90, hjust = 1))
```

*Comment on the plot*

* The plot shows the estimated OR and confidence intervals for solving homicides, comparing male to female victims in each cities and we are 95% confidence that the true OR lies between the confidence intervals. If the confidence interval cross y=1, then there's no significant evidence of a difference in the odds of solving homicides between male and female victims.That is the case 15 out of 47 cities. 
* We also see that most of the estimated OR is less than 1, which suggests that in most states male victims' homicides are less likely to be solved compared to female victims' homicides in that city. That's the case for all evidence of a difference in the odds of solving homicides between male and female victims. For the 3 cities with estimated OR above 1, they all have CI including the value of 1 that suggested no true difference. 
* Some cities also have wide confidence intervals, which is the cities with CI cross the value of 1, which could indicate a small sample size or high variability within the data for those cities, which may be the causes for insignificant results. 

